Blockchain System

### 2020-11-25 papers/execution-model/model.tex
after-meeting

\begin{definition}%[Program]
\emph{Programs} are defined by the following grammar:
\begin{align*}
	\PROGRAM & :: =  \VARIABLE\ \mid \VALUE \mid \lambda \VARIABLE \PROGRAM\ 
	\\&\mid \PROGRAM\PROGRAM\ \mid (\PROGRAM,\PROGRAM) 	%\mid \NI \EI
	\\&\mid \PROGRAM\ \PLUS\ \PROGRAM\ \mid \PROGRAM\ \MINUS\ \PROGRAM\ \mid \PROGRAM\ \EQUAL\ \PROGRAM\ \mid \PROGRAM\ \LESS\ \PROGRAM
	\\&\mid \PROGRAM\ \AND\ \PROGRAM\ \mid \PROGRAM\ \OR\ \PROGRAM\ \mid \NOT\ \PROGRAM
	\\&\mid \NIL\ \mid \CONS\ \PROGRAM \PROGRAM
	\\&\mid \lambda \VARIABLE\QRY
\end{align*}
\end{definition}

\begin{definition}%[State of a node]
  The \emph{state of a node} is a tuple
  $\NODE = [ \PROGRAMS, \ACCOUNTS, \OPERATIONS]$, where $\PROGRAMS$ is the set of the programs, $\ACCOUNTS$ is a set of
  accounts, and
  $\OPERATIONS$ is a set of operations.
\end{definition}

@@

@@

\begin{mathpar}
  \inferrule[Node-Op]
  {
    \Angle{\PAK,\OP.\PUK} \in \ACCOUNTS
  }{
    [\PROGRAMS, \ACCOUNTS, \OPERATIONS]
    \NodeTrans
    [\PROGRAMS, \ACCOUNTS, \OP:: \OPERATIONS]
  }

  \inferrule[Node-Oph]
  {
   \\
  }{
    [\epsilon[\OP] :: \PROGRAMS, \ACCOUNTS, \OPERATIONS]
    \NodeTrans
    [\epsilon[\OPH] :: \PROGRAMS, \ACCOUNTS, \OPERATIONS]
  }

@@

  }{[\epsilon[\GETBALANCE\PUK] :: \PROGRAMS, \ACCOUNTS, \OPERATIONS]  \| \BLOCKCHAIN
    \NodeTrans [\epsilon[\BAL] ::\PROGRAMS, \ACCOUNTS, \OPERATIONS]  \| \BLOCKCHAIN}

@@

  }{[\epsilon[\GETBALANCE\PUH] :: \PROGRAMS, \ACCOUNTS, \OPERATIONS]  \| \BLOCKCHAIN
    \NodeTrans [\epsilon[\BAL] ::\PROGRAMS, \ACCOUNTS, \OPERATIONS]  \| \BLOCKCHAIN}

@@

  }{[\epsilon[\GETSTORAGE\PUH] :: \PROGRAMS, \ACCOUNTS, \OPERATIONS]  \| \BLOCKCHAIN
    \NodeTrans [\epsilon[\STORAGE] ::\PROGRAMS, \ACCOUNTS, \OPERATIONS]  \| \BLOCKCHAIN}

@@

  }{[\epsilon[\GETCODE\PUH] :: \PROGRAMS, \ACCOUNTS, \OPERATIONS]  \| \BLOCKCHAIN
    \NodeTrans [\epsilon[\CODE] ::\PROGRAMS, \ACCOUNTS, \OPERATIONS]  \| \BLOCKCHAIN}

@@

  }{[\epsilon[\GETCOUNTER\PUK] :: \PROGRAMS, \ACCOUNTS, \OPERATIONS]  \| \BLOCKCHAIN
    \NodeTrans [\epsilon[\COU] ::\PROGRAMS, \ACCOUNTS, \OPERATIONS]  \| \BLOCKCHAIN}

@@

  }{[\epsilon[\GETSTATUS\OPH] :: \PROGRAMS, \ACCOUNTS, \OPERATIONS]  \| \BLOCKCHAIN
    \NodeTrans [\epsilon[\STATUSPENDING] ::\PROGRAMS, \ACCOUNTS, \OPERATIONS]  \| \BLOCKCHAIN}

@@

  }{[\epsilon[\GETSTATUS\OPH] :: \PROGRAMS, \ACCOUNTS, \OPERATIONS]  \| \BLOCKCHAIN
    \NodeTrans [\epsilon[\STATUSINCLUDING] ::\PROGRAMS, \ACCOUNTS, \OPERATIONS]  \| \BLOCKCHAIN}

>>>>

\begin{definition}%[Program]
\emph{Expressions} are defined by the following grammar:
\begin{align*}
  \CONSTANT & ::= \ADDR \mid \OPH \mid \PUH \mid\PUK \mid \CODE \mid
              \NTEZ \mid \SUNIT \mid \FALSE \mid \TRUE \\
	\EXPR & :: =  \CONSTANT \mid \VARIABLE \mid \lambda \VARIABLE. \EXPR\ 
	\mid \EXPR\EXPR \mid (\EXPR,\EXPR) \mid \FST\ \EXPR \mid \SND\ \EXPR 	%\mid \NI \EI
	\\&\mid \EXPR\ \PLUS\ \EXPR\ \mid \EXPR\ \MINUS\ \EXPR\ \mid \EXPR\ \EQUAL\ \EXPR\ \mid \EXPR\ \LESS\ \EXPR
	\\&\mid \EXPR\ \AND\ \EXPR\ \mid \EXPR\ \OR\ \EXPR\ \mid \NOT\ \EXPR
  \\&\mid \NIL\ \mid \CONS\ \EXPR\ \EXPR \mid \LEFT\ \EXPR \mid\RIGHT\
  \EXPR \mid \SOME\ \EXPR \mid \NONE
  \\& \mid \RAISE\ \EXPR \mid \TRY\ \EXPR\ \EXCEPT\ \EXPR
  \\& \mid \MATCH\ \EXPR\ \WITH\ \PATTERN\to\EXPR \dots
  \\& \mid \TRANSFER[\EXPR]\EXPR\EXPR\EXPR\EXPR
  \\& \mid \ORIGINATE\EXPR\EXPR\EXPR\EXPR\EXPR
  \\&\mid \QOP\  \EXPR\\
  \QOP & ::= balance \mid status \mid storage \mid code \mid counter
\end{align*}
\end{definition}

\begin{definition}%[State of a node]
  The \emph{state of a node} is a tuple
  $\NODE = [ \EXPRS, \ACCOUNTS, \OPERATIONS]$, where $\EXPRS$ is the set of the programs, $\ACCOUNTS$ is a set of
  accounts, and
  $\OPERATIONS$ is a set of operations.
\end{definition}

@@

\begin{mathpar}
  \inferrule[Node-Opp]
    {
    \Angle{\PAK,\OP.\PUK} \in \ACCOUNTS
  }{
    [\EC\OP :: \EXPRS, \ACCOUNTS, \OPERATIONS] \NodeTrans
    [\EXPRS, \ACCOUNTS, (\EC{},\OP):: \OPERATIONS]
  }
\end{mathpar}

\begin{mathpar}
  \inferrule{
    \CHECKBAL (\MANAGERS, \PUK, \NTEZ, \MTEZ) \\
    \CHECKCOU (\MANAGERS, \PUK) \\
    \CHECKPUB (\MANAGERS, \PUK') \\
    \CHECKGAS (\PUK, \PUK', \NTEZ, \MTEZ) \\
    \OP = \TRANSFER\NTEZ\PUK{\PUK'}\MTEZ \\
    \OPH = \GENERATEOPH (\PUK, \PUK', \NTEZ, \MTEZ, \TIME)
  }{
   { [\EXPRS, \ACCOUNTS, (\EC{},\OP) :: \OPERATIONS] \| [\PENDING,
     \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME] } \SystemTrans \\
   { [\EC{?\OPH}  :: \EXPRS, \ACCOUNTS, \OPERATIONS] \|
     [ \Angle{\OP,\OPH, \TIME}
     ::\PENDING,
     \ACCEPTED,
     \UPDATECOU(\MANAGERS, \PUK, \TRUE),
     \CONTRACTORS,
     \TIME]
   }
  }
\end{mathpar}

@@

\begin{mathpar}
  \inferrule[Node-Op]
  {
    \Angle{\PAK,\OP.\PUK} \in \ACCOUNTS
  }{
    [\EXPRS, \ACCOUNTS, \OPERATIONS]
    \NodeTrans
    [\EXPRS, \ACCOUNTS, \OP:: \OPERATIONS]
  }

  \inferrule[Node-Oph]
  {
   \\
  }{
    [\EC\OP :: \EXPRS, \ACCOUNTS, \OPERATIONS]
    \NodeTrans
    [\EC\OPH :: \EXPRS, \ACCOUNTS, \OPERATIONS]
  }

@@

  }{[\epsilon[\GETBALANCE\PUK] :: \EXPRS, \ACCOUNTS, \OPERATIONS]  \| \BLOCKCHAIN
    \NodeTrans [\epsilon[\BAL] ::\EXPRS, \ACCOUNTS, \OPERATIONS]  \| \BLOCKCHAIN}

@@

  }{[\epsilon[\GETBALANCE\PUH] :: \EXPRS, \ACCOUNTS, \OPERATIONS]  \| \BLOCKCHAIN
    \NodeTrans [\epsilon[\BAL] ::\EXPRS, \ACCOUNTS, \OPERATIONS]  \| \BLOCKCHAIN}

@@

  }{[\epsilon[\GETSTORAGE\PUH] :: \EXPRS, \ACCOUNTS, \OPERATIONS]  \| \BLOCKCHAIN
    \NodeTrans [\epsilon[\STORAGE] ::\EXPRS, \ACCOUNTS, \OPERATIONS]  \| \BLOCKCHAIN}

@@

  }{[\epsilon[\GETCODE\PUH] :: \EXPRS, \ACCOUNTS, \OPERATIONS]  \| \BLOCKCHAIN
    \NodeTrans [\epsilon[\CODE] ::\EXPRS, \ACCOUNTS, \OPERATIONS]  \| \BLOCKCHAIN}

@@

  }{[\epsilon[\GETCOUNTER\PUK] :: \EXPRS, \ACCOUNTS, \OPERATIONS]  \| \BLOCKCHAIN
    \NodeTrans [\epsilon[\COU] ::\EXPRS, \ACCOUNTS, \OPERATIONS]  \| \BLOCKCHAIN}

@@

  }{[\epsilon[\GETSTATUS\OPH] :: \EXPRS, \ACCOUNTS, \OPERATIONS]  \| \BLOCKCHAIN
    \NodeTrans [\epsilon[\STATUSPENDING] ::\EXPRS, \ACCOUNTS, \OPERATIONS]  \| \BLOCKCHAIN}

@@

  }{[\epsilon[\GETSTATUS\OPH] :: \EXPRS, \ACCOUNTS, \OPERATIONS]  \| \BLOCKCHAIN
    \NodeTrans [\epsilon[\STATUSINCLUDING] ::\EXPRS, \ACCOUNTS, \OPERATIONS]  \| \BLOCKCHAIN}
